Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-05 paper/abstract.tex
pass on intro

\textbf{Context.} 
JavaScript is a very popular programming language today with several
implementations competing for market dominance. Although a
specification document and a conformance test suite exist to guide
engine development, bugs occur and have important practical
consequences. Implementing correct
engines is challenging because the spec is intentionally
incomplete and evolves frequently.
\textbf{Objective.} 
This paper investigates the use of test transplantation and differential testing
for revealing functional bugs in JavaScript engines.
The former technique runs test suites of a given engine on another engine. 
The latter technique fuzzes existing inputs 
and then compares the output produced by different engines with a differential oracle.
\textbf{Method.} 
We conducted experiments with engines from four major players
--Apple, Google, Microsoft, and Mozilla--to assess the effectiveness of 
test transplantation and differential testing.
\textbf{Results.} 
Our results indicate that both techniques revealed several bugs, many of which
confirmed by developers. We reported \noBugsTransplantation{} bugs
with test transplantation (\noBugsTransplantationConfirmed{} of these bugs
confirmed and \noBugsTransplantationFixed{} fixed) and reported
\noBugsDifferentialTesting{} bugs with differential testing
(\noBugsDifferentialTestingConfirmed{} of these confirmed
and \noBugsDifferentialTestingFixed{} fixed). Results indicate that
most of these bugs affected two engines--Apple's
\jsc{} and Microsoft's \chakra{}. 
To summarize, our results show that
test transplantation and differential testing
are easy to apply and very effective in
finding bugs in complex software, such as JavaScript engines.

>>>>

\textbf{Context.}
JavaScript is a popular programming language today with several
implementations competing for market dominance. Although a
specification document and a conformance test suite exist to guide
engine development, bugs occur and have important practical
consequences. Implementing correct
engines is challenging because the spec is intentionally
incomplete and evolves frequently.
\textbf{Objective.}
This paper investigates the use of test transplantation and
differential testing for revealing functional bugs in JavaScript
engines.  The former technique runs the regression test suite of a
given engine on another engine.  The latter technique fuzzes existing
inputs and then compares the output produced by different engines with
a differential oracle.
\textbf{Method.}
We conducted experiments with engines from five major players--Apple,
Google, Microsoft, Facebook, and Mozilla--to assess the effectiveness
of test transplantation and differential testing.
\textbf{Results.}
Our results indicate that both techniques revealed several bugs, many of which
confirmed by developers. We reported \noBugsTransplantation{} bugs
with test transplantation (\noBugsTransplantationConfirmed{} of these bugs
confirmed and \noBugsTransplantationFixed{} fixed) and reported
\noBugsDifferentialTesting{} bugs with differential testing
(\noBugsDifferentialTestingConfirmed{} of these confirmed
and \noBugsDifferentialTestingFixed{} fixed). Results indicate that
most of these bugs affected two engines--Apple's
\jsc{} and Microsoft's \chakra{}.
To summarize, our results show that
test transplantation and differential testing
are easy to apply and very effective in
finding bugs in complex software, such as JavaScript engines.

### 2020-06-05 paper/paper.tex
pass on intro

\author{Igor Lima \and Breno Miranda\footnotemark \and Marcelo d'Amorim}
%\authorrunning{Short form of author list} % if too long for running head

\institute{
* Corresponding author: Breno Miranda \and \email{bafm@cin.ufpe.br}\\ \\
Igor Lima \and \email{isol2@cin.ufpe.br} \\
Breno Miranda \and \email{bafm@cin.ufpe.br} \\
Marcelo d'Amorim \and \email{damorim@cin.ufpe.br} \\
\at Universidade Federal de Pernambuco, Recife, PE, Brazil}

@@

JavaScript (\js{}) is one of the most popular programming languages
today~\cite{stackify,redmonk-javascript}, with penetration in various software development segments including, web, mobile,
and, more recently, the Internet of
Things~(IoT)~\cite{simply-technologies}. The interest of the community
for the language encourages constant improvements in its specification~\cite{ecmas262-spec}. It is natural to expect that such improvements
lead to sensible changes in engine implementations~\cite{kangax}. Even small
changes can have high practical impact. For example, in October 2014 a
new attribute added to Array objects resulted in the MS Outlook
Calendar web app, which is built in \js{}, to fail under
Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}.

Finding bugs in \js\ engines is an important problem given the range
of applications that could be affected with those bugs. It is also
challenging.  Specifications are intentionally incomplete as to enable
development flexibility. In addition, they evolve frequently to
accommodate the pressing demands from
developers~\cite{ecmas262-spec-repo}. An official conformance test
suite exists for \js~\cite{tc39-github}, but, naturally, many test
scenarios are not covered in the suite. In addition, we noticed that a
significant fraction (5 to 15\%) of the tests fail regularly in the
most popular engines, reflecting the struggle of developers in keeping
up with the pace of spec evolution (see Table~\ref{tab:test262}).

@@

\item \emph{Cross-engine differential testing}.
  This technique fuzzes existing test
  inputs~\cite{fuzz-testing-history} and then compares the output
  produced by different engines using a differential
  oracle. The intuition is that interesting inputs can be created
  from existing inputs and multiple engines can be used to address the
  lack of oracles.
\end{itemize}

The study measures the ability of these techniques in finding bugs and
the impact of false positives on their practicality.

@@

%% It automates test generation in scenarios where multiple
%% implementations of a system exist. DT leverages diversity across
%% system's implementations to detect anomalous behavior.
%\emph{Related Ideas.}~The idea of test set diversity dates back to the
%eighties~\cite{white-cohen-tse1980,ostrand-balcer-1988}. In contrast
%to prior work on this topic, this paper explores diversity of
%implementations and diversity of sources of test cases as opposed to
%diversity of the test cases themselves. Section~\ref{sec:related:diversity-testing}
%elaborates related work on this topic.
%
\emph{Related Ideas.}~Differential Testing~\cite{Brumley-etal-ss07} (DT)
has been applied in a variety of contexts to find
bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}.
It has shown to be specially practical in scenarios where the
observation of difference gives a strong signal of a real problem. For
example, Mozilla runs JS files against different configurations of a
given build of their \smonkey\ engine (\eg{}, trying to enable or not
eager JIT compilation\footnote{These files are created with the
  grammar-based fuzzer jsfunfuzz~\cite{jsfunfuzz}. Look for option
  ``compare\_jit'' from funfuzz.}). A positive aspect of the approach
is that it can be fully automated---as only one engine is used, the
outcomes of the test in both configurations are expected to be
identical. The Mozilla team uses this approach since 2002; they have
been able to find over 270 bugs since
then~\cite{jsfunfuzz-at-mozilla}, including security
bugs. Cross-engine differential testing, in contrast, has not been
widely popularized. One possible reason is that it is still not
practical to fully automate the technique. In contrast to other
applications of differential testing, a number of legitimate reasons
exist, other than a bug, for a test execution to manifest discrepancy
(see Tables~\ref{fig:piecharts-transplantation} and
~\ref{tab:false-positives}). Variations of these ideas have
been explored before in different contexts.  The goal of the paper is
to assess the ability of the techniques aforementioned in finding bugs
on \javascript\ engines.

@@

\sloppy \emph{Results.}~We considered the following engines--\chakra{}
(Microsoft), JavaScriptCore (Apple), \veight{} (Google),
\smonkey{} (Mozilla), and \hermes (Facebook). Figure~\ref{fig:summary} shows the breakdown of bug reports per engine (\ref{fig:stacked-engine}) and per technique
(\ref{fig:stacked-technique}).
\Fix{Jefferson, atualize a figura!}
Each stacked bar breaks down the bugs
per status (\eg{}, ``1-New''). The prefix number indicates the
ordering that status labels are assigned. Several of these
reports have the label ``3-Fixed'', indicating that bug fixes have
been incorporated into the code already. Note that most of these bugs
affected two engines--\chakra{} and JavaScriptCore (\jsc{}).  We
reported \noBugsBugsReportedGoogle{} bugs in \veight{}
(\noBugsBugsConfirmedGoogle{} confirmed) and none in \smonkey{}.
Furthermore, our results show that both techniques revealed several
bugs, most of which confirmed by developers. Test transplantation
revealed \noBugsTransplantation{} bugs (of which,
\noBugsTransplantationConfirmed{} were confirmed and
\noBugsTransplantationFixed{} were fixed) whereas differential testing
revealed \noBugsDifferentialTesting{} bugs (of which,
\noBugsDifferentialTestingConfirmed{} were confirmed and
\noBugsDifferentialTestingFixed{} were fixed).  Overall, results
indicate that both techniques were successful at finding bugs. The
number of bug reports were similar, if we consider only those
confirmed or fixed. Most bugs we found are of moderate severity.

@@

\emph{Key Findings.}~The list of findings of this work includes--1)
Not only multiple different implementations can be leveraged in
differential testing, but differences in test suites can also be
important. 2) Even for problems with fairly clear specifications, as
in \javascript{}, there is likely to be (a lot of) variation between
different implementations. 3) Differential testing is feasible on
real, complex, widely used pieces of
software. Section~\ref{sec:lessons} expands and elaborates key
findings and lessons learned.

%% LIST OF CONTRIBUTIONS
\emph{Contributions.}~The most important contribution of this work is empirical:
we provide a comprehensive study analyzing the effectiveness of
test transplantation and differential testing
in revealing functional bugs in popular \javascript\ engines.
Additional contributions are:
1)~A number of bugs found and fixed.
We reported a total of \totalBugsReported{} bugs.
Of these, \totalBugsConfirmed{} bugs were confirmed and \totalBugsFixed{} bugs were fixed.
2)~An infrastructure for performing test transplantation and differential testing.
The scripts to run the experiments will be available upon request.
The data is publicly available \dataRepo{}.

\vspace{1ex} To summarize, this paper provides initial, yet strong evidence
that exploring test transplantation and differential testing
should be encouraged to find functional bugs
in JavaScript engines.

>>>>

\author{Jefferson Silva \and Igor Lima \and Breno Miranda\footnotemark
  \and Gustavo Pinto \and Marcelo d'Amorim}
%\authorrunning{Short form of author list} % if too long for running head

\institute{
* Corresponding author: Breno Miranda \and \email{bafm@cin.ufpe.br}\\ \\
Jefferson Silva \and \email{jefferson.alves.silva@icen.ufpa.br}\\
Igor Lima \and \email{isol2@cin.ufpe.br} \\
Gustavo Pinto \and \email{gpinto@ufpa.br} \\
Breno Miranda \and \email{bafm@cin.ufpe.br} \\
Marcelo d'Amorim \and \email{damorim@cin.ufpe.br} \\
\at Universidade Federal de Pernambuco, Recife, PE, Brazil}

@@

JavaScript (\js{}) is one of the most popular programming languages
today~\cite{stackify,redmonk-javascript}, with penetration in various
software development segments including, web, mobile, and, more
recently, the Internet of Things~(IoT)~\cite{simply-technologies}. The
interest of the community for the language encourages constant
improvements in its specification~\cite{ecmas262-spec}. It is natural
to expect that such improvements lead to sensible changes in engine
implementations~\cite{kangax}. Even small changes can have high
practical impact. For example, in October 2014 a new attribute added
to Array objects resulted in the MS Outlook Calendar web app to fail
under Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}.

Finding bugs in \js\ engines is an important problem given the range
of applications that could be affected with those bugs. It is also
challenging.  Specifications are intentionally incomplete as to enable
development flexibility. In addition, they evolve frequently to
accommodate the pressing demands from
developers~\cite{ecmas262-spec-repo}. An official conformance test
suite exists for \js~\cite{tc39-github}, but, naturally, many test
scenarios are not covered in the suite. In addition, we noticed that a
significant fraction (5 to 15\%) of the tests in that stuite fail
regularly in the most popular engines, reflecting the struggle of developers in keeping
up with the pace of spec evolution (see Table~\ref{tab:test262}).

@@

\item \emph{Cross-engine differential testing}.  This technique fuzzes
  existing test inputs~\cite{fuzz-testing-history} and then compares
  the output produced by different engines using a differential
  oracle. The intuition is that interesting inputs can be created from
  existing inputs and multiple engines can be used to address the lack
  of oracles for the newly created inputs.
\end{itemize}

The study measures the ability of these techniques in finding bugs and
the impact of false positives on their practicality. \Mar{seria bom
  adicionar uma frase com rationale para escolha destas tecnicas.}

@@

%% It automates test generation in scenarios where multiple
%% implementations of a system exist. DT leverages diversity across
%% system's implementations to detect anomalous behavior.
%\emph{Related Ideas.}~The idea of test set diversity dates back to the
%eighties~\cite{white-cohen-tse1980,ostrand-balcer-1988}. In contrast
%to prior work on this topic, this paper explores diversity of
%implementations and diversity of sources of test cases as opposed to
%diversity of the test cases themselves. Section~\ref{sec:related:diversity-testing}
%elaborates related work on this topic.
%
\emph{Related Ideas.}~Differential Testing~\cite{Brumley-etal-ss07}
(DT) has been applied in a variety of contexts to find
bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}.
It has shown to be specially practical in scenarios where the
observation of difference gives a strong signal of a real problem. For
example, Mozilla runs JS files against different configurations of a
given build of their \smonkey\ engine (\eg{}, trying to enable or not
eager JIT compilation\footnote{These files are created with the
  grammar-based fuzzer jsfunfuzz~\cite{jsfunfuzz}. Look for option
  ``compare\_jit'' from funfuzz.}). A positive aspect of the approach
is that it can be fully automated---as only one engine is used, the
outcomes of the test in both configurations are expected to be
identical. The Mozilla team uses this approach since 2002; they have
been able to find over 270 bugs since
then~\cite{jsfunfuzz-at-mozilla}, including security
bugs. Cross-engine differential testing, in contrast, has not been
widely popularized because the reported differences are more unlikely
to be false alarms. In this context, a number of legitimate reasons
exist, other than a bug, for a test execution to manifest discrepancy
(see Tables~\ref{fig:piecharts-transplantation} and
~\ref{tab:false-positives}). As consequence, humans need to inspect
the reports.

%Variations of these ideas have been explored before in different contexts.

%It is important to note that the goal of the paper is to assess the
%ability of the techniques aforementioned in finding bugs on \javascript\ engines.

@@

\sloppy \emph{Results.}~Our study considered the following
engines--\chakra{}~(Microsoft), \hermes~(Facebook),
JavaScriptCore~(Apple), \smonkey{}~(Mozilla), and
\veight{}~(Google). Figure~\ref{fig:summary} shows the breakdown of
bug reports per engine (\ref{fig:stacked-engine}) and per technique
(\ref{fig:stacked-technique}).  \Fix{Jefferson, atualize a figura!
  Estranho nao ter pilha para as 5 engines.}  Each stacked bar breaks
down the bugs per status (\eg{}, ``1-New''). The number indicates the
ordering that status labels are assigned by developers: ``New'', then
``Confirmed'', then ``Fixed''. Several of these reports have the label
``3-Fixed'', indicating that bug fixes have been incorporated into the
code already. Note that most of these bugs affected two
engines--\chakra{} and JavaScriptCore (\jsc{}).  We reported
\noBugsBugsReportedGoogle{} bugs in \veight{}
(\noBugsBugsConfirmedGoogle{} confirmed) and none in \smonkey{}.
Furthermore, our results show that both techniques revealed several
bugs, most of which confirmed by developers. Test transplantation
revealed \noBugsTransplantation{} bugs (of which,
\noBugsTransplantationConfirmed{} were confirmed and
\noBugsTransplantationFixed{} were fixed) whereas differential testing
revealed \noBugsDifferentialTesting{} bugs (of which,
\noBugsDifferentialTestingConfirmed{} were confirmed and
\noBugsDifferentialTestingFixed{} were fixed).  Overall, results
indicate that both techniques were successful at finding bugs. The
number of bug reports were similar, if we consider only those
confirmed or fixed. Most bugs we found are of moderate severity.

@@

\emph{Key Findings.}~We found that--1)~Differential testing and Test
Transplation are practical and effective to find bugs on real,
complex, and widely used pieces of software, 2)~Even for problems with
fairly clear specifications, as in \javascript{}, there is likely (a
lot of) variation between different
implementations. Section~\ref{sec:lessons} expands and elaborates key
findings and lessons learned.

%% LIST OF CONTRIBUTIONS
\emph{Contributions.}~The most important contribution of this work is
empirical: we provide a comprehensive study analyzing the
effectiveness of two practical techniques in revealing functional bugs
in popular \javascript\ engines. The results of the study include:
1)~A number of bugs found and fixed and 2)~An infrastructure for
performing test transplantation and differential testing. Our data and
tools are publicly available under the following link:

\dataRepo{}.

\vspace{1ex} To summarize, this paper provides initial, yet strong
evidence, that exploring test transplantation and differential testing
is practical to find functional bugs in JavaScript engines and should
be encouraged.
